---
title: "manually test calculations of the recommended interventions with BB data and proportions as a continuous outcome."
output: pdf_document
date: "`r Sys.Date()`"
author: "Ante Bing"
editor_options: 
  chunk_output_type: console
---
## We manually test the calculations of the recommended interventions with the BetterBirth data.

## install and Load the LAGO pacakge 
```{r}
devtools::clean_dll()
devtools::load_all()
```

## Load the BetterBirth data with EBP proportions
```{r}
# BB data has been open sourced, so it has been preloaded
bb_proportions <- LAGO::BB_proportions
head(bb_proportions)
```

## Calculate the recommended interventions using the LAGO package 
```{r}
# using a linear cost function
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  center_characteristics = c("birth_volume_100"),
  center_characteristics_optimization_values = 1.75,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 1.7), c(0, 8)),
  outcome_goal = 0.8,
  include_confidence_set = TRUE
)
# for higher order cost, see test_higher_order_costs.Rmd
```

## Compare with the results from Bing et al. 
```{r}
# From Bing et al paper:
# "... For a center with an average birth volume (z = 175), the estimated
# optimal intervention package under the linear cost function comprised a launch
# duration of 5 days and 31 coaching visits ... "
optimization_results$rec_int
# 30.52 approximates to 31, so same results as described in the paper

# cost for the recommended interventions
optimization_results$rec_int_cost

# estimated outcome mean/probability in the next stage
optimization_results$est_outcome_goal
```

## continuous outcome should also work with
## fixed center effects 
## fixed time effects 
## additional covariates 
## interaction terms 
```{r}
# add fake center effects
set.seed(123)
bb_proportions$center <- sample(1:10, nrow(bb_proportions), replace = TRUE)

## add fake time effects
bb_proportions$period <- sample(1:10, nrow(bb_proportions), replace = TRUE)

## add fake additional covariates
bb_proportions$MI_coaching <- sample(0:1, nrow(bb_proportions), replace = TRUE)

## add fake interaction term
bb_proportions$`coaching_updt:launch_duration` <-
  bb_proportions$coaching_updt * bb_proportions$launch_duration

head(bb_proportions)
```

```{r}
devtools::clean_dll()
devtools::load_all()
```

```{r}
# only add center effects
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  include_center_effects = TRUE,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE
)
```

```{r}
# center effects, but LAGO optimization is for a specific center
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  include_center_effects = TRUE,
  center_effects_optimization_values = "5",
  intervention_lower_bounds = c(0, 0),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE
)
```

```{r}
# center effects, but LAGO optimization is for a specific center
# different center
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  include_center_effects = TRUE,
  center_effects_optimization_values = "8",
  intervention_lower_bounds = c(0, 0),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE
)
```

```{r}
# center effects, but LAGO optimization is for a specific center
# grid search method
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  include_center_effects = TRUE,
  center_effects_optimization_values = "5",
  intervention_lower_bounds = c(0, 0),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE,
  optimization_method = "grid_search",
  optimization_grid_search_step_size = c(1, 1)
)
```

```{r}
# add center effects, and time effects
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  include_center_effects = TRUE,
  include_time_effects = TRUE,
  time_effect_optimization_value = 10,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE
)
```

```{r}
# add center effects, and time effects
# center specific optimization
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  include_center_effects = TRUE,
  center_effects_optimization_values = "8",
  include_time_effects = TRUE,
  time_effect_optimization_value = 10,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = FALSE
)
```

```{r}
# add center effects, time effects, and additional covariates
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  additional_covariates = c("MI_coaching"),
  include_center_effects = TRUE,
  include_time_effects = TRUE,
  time_effect_optimization_value = 10,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE
)
```

```{r}
# add center effects, time effects, and additional covariates
# center specific optimization
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c("coaching_updt", "launch_duration"),
  additional_covariates = c("MI_coaching"),
  include_center_effects = TRUE,
  center_effects_optimization_values = "2",
  include_time_effects = TRUE,
  time_effect_optimization_value = 10,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.6,
  include_confidence_set = TRUE
)
```

```{r}
devtools::clean_dll()
devtools::load_all()
```
```{r}
# add center effects, time effects, additional covariates,
# and interaction terms
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c(
    "coaching_updt",
    "launch_duration",
    "coaching_updt:launch_duration"
  ),
  include_interaction_terms = TRUE,
  main_components = c("coaching_updt", "launch_duration"),
  additional_covariates = c("MI_coaching"),
  include_center_effects = TRUE,
  include_time_effects = TRUE,
  time_effect_optimization_value = 10,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.8,
  include_confidence_set = TRUE
)
```


```{r}
# add center effects, time effects, additional covariates,
# and interaction terms
# center specific optimization
optimization_results <- lago_optimization(
  data = bb_proportions,
  outcome_name = "EBP_proportions",
  outcome_type = "continuous",
  glm_family = "quasibinomial",
  link = "logit",
  intervention_components = c(
    "coaching_updt",
    "launch_duration",
    "coaching_updt:launch_duration"
  ),
  include_interaction_terms = TRUE,
  main_components = c("coaching_updt", "launch_duration"),
  additional_covariates = c("MI_coaching"),
  include_center_effects = TRUE,
  center_effects_optimization_values = "5",
  include_time_effects = TRUE,
  time_effect_optimization_value = 10,
  intervention_lower_bounds = c(1, 1),
  intervention_upper_bounds = c(40, 5),
  cost_list_of_vectors = list(c(0, 380, -24, 0.6), c(0, 1700, -950, 220)),
  outcome_goal = 0.8,
  include_confidence_set = TRUE
)
```
